Numerical Solution of Point Defect Equations by MOOSE

### 2020-11-20 examples/point_defects/article/article.tex
article latex file

\documentclass[a4paper]{article}
\usepackage[margin=25mm]{geometry}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\pagenumbering{gobble}
\usepackage{verbatim}

@@

\title{Numerical Solution of Point Defect Equations by MOOSE}
\author{Abdurrahman Ozturk$^{1}$, Karim Ahmed$^{1}$  \\
        \small $^{1}$Texas A\&M University \\
        % \small $^{2}$University B \\
}
% \date{} % Comment this line to show today's date

\begin{document}
\maketitle

@@

%TC:ignore
\keywords{point defect equations, rate theory, radiation damage, MOOSE}
% \begin{thebibliography}{00}
% \bibitem{b2} Garry Was.
% \end{thebibliography}
%TC:endignore

@@

@@

@@

The production bias is a factor that is used to create a difference between interstitial
and vacancy generation in domain. As the production bias increases, vacancy production
increases and the gap between steady state vacancy and interstitial concentrations gets wider.
Most of the plots in this part are generated by using the simulation results for Cs=1e18 m -3 ,
T=773K, K 0 =1e-3 dpa/s.
In nano-scale case, since the domain size is not big enough, the boundaries become
closer to each other. This causes point defects to reach sinks before they react with each other
and recombination plateau to disappear as it can be seen in Fig. 2. The nanoscale case acts like
a high-sink and high-temp condition case despite its low-sink and low-temperature. Therefore,
change in production bias does not have a significant effect on average concentration behavior
in nanoscale

@@

The defect production rate (K 0 ) is the source term in point defect equations and has a
significant effect on concentrations.
In nano-scale case, the average concentration behavior is like high-sink density behavior
because of narrow domain. But, when the defect production rate increases, the average
concentration is shifted upward, and interstitial and vacancy average concentrations get closer
to each other because the production compensates more absorption at sinks than previous.
Based on this, if the production rate increased sufficiently, the recombination zone would
appear again in nano-scale domain.

>>>>

\documentclass[a4paper]{article}
\usepackage[margin=25mm]{geometry}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{verbatim}
\pagenumbering{arabic}
\graphicspath{ {./plots/} }

@@

% \tableofcontents

\title{Numerical Solution of Point Defect Equations by MOOSE}
\author{Abdurrahman Ozturk$^{1}$, Karim Ahmed$^{1}$  \\
        \small $^{1}$Texas A\&M University \\
        % \small $^{2}$University B \\
}
% \date{} % Comment this line to show today's date
\begin{document}
\maketitle

@@

%TC:ignore
\keywords{point defect equations, rate theory, radiation damage, MOOSE}
%TC:endignore

@@

% \listoftables
% \listoffigures

@@

\begin{table}[h!]
  \centering
  \caption{Material Properties for Nickel\cite{walgraef1996}}
  \label{table:1}
  \begin{tabular}{ ||p{2cm}|p{2cm}||  }
     % \hline
     % \multicolumn{5}{|c|}{Material Properties} \\
     \hline
     Property & Value\\
     \hline\hline
     a  & 0.352 nm\\
     V  & 0.01206 nm^3\\
     E_{m,i}  & 0.30 eV\\
     E_{m,v}  & 1.30 eV\\
     E_{f,i}  & 4.27 eV\\
     E_{f,v}  & 1.60 eV\\
     D_{0,i}  & 1e-7 m^2/s\\
     D_{0,v}  & 6e-5 m^2/s\\

     \hline
  \end{tabular}
\end{table}

\begin{table}[h!]
  \centering
  \caption{Simulation Parameters}
  \label{table:2}
  \begin{tabular}{ ||p{2cm}|p{2cm}|p{4cm}|p{2cm}|p{2cm}||  }
     % \multicolumn{5}{|c|}{Simulation Parameters} \\
     \hline
     Type & Dose Rate & Defect Production Profile & Temperature & Sink Density\\
     \hline
     \hline
     Neutron  & 1e-3  & Uniform     & 773K & 1e18\\
              & 1e-6  & Uniform     & 773K & 1e18\\
     \hline
     Ion      & 1e-3  & Distributed & 773K & 1e18\\
              & 1e-6  & Distributed & 773K & 1e18\\
     \hline
  \end{tabular}
\end{table}

@@

The production bias is a factor that is used to create a difference between interstitial
and vacancy generation in domain. As the production bias increases, vacancy production
increases and the gap between steady state vacancy and interstitial concentrations gets wider.
Most of the plots in this part are generated by using the simulation results for Cs=1e18 m -3 ,
T=773K, K 0 =1e-3 dpa/s.

  \subsection{Neutron Irradiation}
    \subsubsection{Concentrations}
      \begin{figure}[h!]  %Neutron - 1e-6 dpa/s - %0 Bias rate
        \centering
        \subfloat{\includegraphics[scale=0.6]{interstitial_concentration_500-5000nm-neutron-0}}
        \qquad
        \subfloat{\includegraphics[scale=0.6]{vacancy_concentration_500-5000nm-neutron-0}}
        \caption{Concentration profiles for 1e-6 dpa/s and 0\% Production Bias}
        \label{figure:1}
      \end{figure}
      \begin{figure}[h!]  %Neutron - 1e-3 dpa/s - %0 Bias rate
        \centering
        \subfloat{\includegraphics[scale=0.6]{interstitial_concentration_500-5000nm-high_neutron-0}}
        \qquad
        \subfloat{\includegraphics[scale=0.6]{vacancy_concentration_500-5000nm-high_neutron-0}}
        \caption{Concentration profiles for 1e-3 dpa/s and 0\% Production Bias}
        \label{figure:2}
      \end{figure}
      \begin{figure}[h!]  %Neutron - 1e-6 dpa/s - %5 Bias rate
        \centering
        \subfloat{\includegraphics[scale=0.6]{interstitial_concentration_500-5000nm-neutron-5}}
        \qquad
        \subfloat{\includegraphics[scale=0.6]{vacancy_concentration_500-5000nm-neutron-5}}
        \caption{Concentration profiles for 1e-6 dpa/s and 5\% Production Bias}
        \label{figure:3}
      \end{figure}
      \begin{figure}[h!]  %Neutron - 1e-3 dpa/s - %5 Bias rate
        \centering
        \subfloat{\includegraphics[scale=0.6]{interstitial_concentration_500-5000nm-high_neutron-5}}
        \qquad
        \subfloat{\includegraphics[scale=0.6]{vacancy_concentration_500-5000nm-high_neutron-5}}
        \caption{Concentration profiles for 1e-3 dpa/s and 5\% Production Bias}
        \label{figure:4}
      \end{figure}
      \begin{figure}[h!]  %Neutron - 1e-3 dpa/s - %5 Bias rate
        \centering
        \subfloat{\includegraphics[scale=0.6]{super_saturation_500-5000nm-neutron-5}}
        \qquad
        \subfloat{\includegraphics[scale=0.6]{super_saturation_500-5000nm-high_neutron-5}}
        \caption{Vacancy Supersaturation profiles for 1e-6 dpa/s and 1e-3 dpa/s with 5\% Production Bias}
        \label{figure:5}
      \end{figure}
    \subsubsection{Sink Strengths}
      \begin{figure}[h!]
        \centering
        \includegraphics[scale=0.6]{concentration_proflies_MOOSE_Analytical_Neutron_0}
        \caption{Comparison of MOOSE results with analytical solution for a 1D spherical grain.\cite{heald1977}}
        \label{figure:6}
      \end{figure}

  \subsection{Ion Irradiation}
    \subsubsection{Concentrations}
      \begin{figure}[h!]  %Ion - 1e-6 dpa/s - %0 Bias rate
        \centering
        \subfloat{\includegraphics[scale=0.6]{interstitial_concentration_500-5000nm-ion-0}}
        \qquad
        \subfloat{\includegraphics[scale=0.6]{vacancy_concentration_500-5000nm-ion-0}}
        \caption{Concentration profiles for 1e-6 dpa/s and 0\% Production Bias}
        \label{figure:7}
      \end{figure}
      \begin{figure}[h!]  %Ion - 1e-3 dpa/s - %0 Bias rate
        \centering
        \subfloat{\includegraphics[scale=0.6]{interstitial_concentration_500-5000nm-low_ion-0}}
        \qquad
        \subfloat{\includegraphics[scale=0.6]{vacancy_concentration_500-5000nm-low_ion-0}}
        \caption{Concentration profiles for 1e-3 dpa/s and 0\% Production Bias}
        \label{figure:8}
      \end{figure}
      \begin{figure}[h!]  %Ion - 1e-6 dpa/s - %5 Bias rate
        \centering
        \subfloat{\includegraphics[scale=0.6]{interstitial_concentration_500-5000nm-ion-5}}
        \qquad
        \subfloat{\includegraphics[scale=0.6]{vacancy_concentration_500-5000nm-ion-5}}
        \caption{Concentration profiles for 1e-6 dpa/s and 5\% Production Bias}
        \label{figure:9}
      \end{figure}
      \begin{figure}[h!]  %Ion - 1e-3 dpa/s - %5 Bias rate
        \centering
        \subfloat{\includegraphics[scale=0.6]{interstitial_concentration_500-5000nm-low_ion-5}}
        \qquad
        \subfloat{\includegraphics[scale=0.6]{vacancy_concentration_500-5000nm-low_ion-5}}
        \caption{Concentration profiles for 1e-3 dpa/s and 5\% Production Bias}
        \label{figure:10}
      \end{figure}
      \begin{figure}[h!]  %Neutron - 1e-3 dpa/s - %5 Bias rate
        \centering
        \subfloat{\includegraphics[scale=0.6]{super_saturation_500-5000nm-ion-5}}
        \qquad
        \subfloat{\includegraphics[scale=0.6]{super_saturation_500-5000nm-low_ion-5}}
        \caption{Vacancy Supersaturation profiles for 1e-6 dpa/s and 1e-3 dpa/s with 5\% Production Bias}
        \label{figure:11}
      \end{figure}

    \subsubsection{Sink Strengths}

In nano-scale case, since the domain size is not big enough, the boundaries become
closer to each other. This causes point defects to reach sinks before they react with each other
and recombination plateau to disappear as it can be seen in Fig. 2. The nanoscale case acts like
a high-sink and high-temp condition case despite its low-sink and low-temperature. Therefore,
change in production bias does not have a significant effect on average concentration behavior
in nanoscale

@@

The defect production rate (K 0 ) is the source term in point defect equations and has a
significant effect on concentrations.
In nano-scale case, the average concentration behavior is like high-sink density behavior
because of narrow domain. But, when the defect production rate increases, the average
concentration is shifted upward, and interstitial and vacancy average concentrations get closer
to each other because the production compensates more absorption at sinks than previous.
Based on this, if the production rate increased sufficiently, the recombination zone would
appear again in nano-scale domain.\cite{was2016}

\section{Conclusion} \hspace{10pt}

% \begin{thebibliography}{00}
% \bibitem{b2} Garry S. Was.
% \end{thebibliography}
\addcontentsline{toc}{section}{References}
\bibliographystyle{unsrt}
\bibliography{ref}
